Contention Management for 5G

### 2017-02-01 article/article.tex
code prime vs 3NT
merge

\graphicspath{{figures/}}
\newcommand\rmatching{${\cal R}$-matching\xspace}
\newcommand\mdelay{$\cal M$-delay\xspace}
\newcommand\matchedgraph{{\bf matched graph}}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newcommand{\reporttitle}{Contention management for Deterministic Networking}     % Titre
\newcommand{\reportauthor}{Maël \textsc{Guiraud }} % Auteur
\newcommand{\reportsubject}{Master Thesis} 
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\setlength{\parskip}{1ex} % Espace entre les paragraphes

@@

   \todo{Definition of the load. La preuve se réfère à la précédente qui n'a pas été retenue, il faut du coup tout expliquer.}

    \begin{theorem}
    Problem PRA cannot be approximated within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
    and $n$ is the number of pairs in the assignment.
    \end{theorem}

    \begin{proof}
    We reduce PRA to graph coloring. Let $G$ be a graph instance of the $k$-coloring problem. 
    We define $H$ in the following way: for each vertex $v$ in $G$, there is a route $r_v$ in $H$.
    Two routes $r_v$ and $r_u$ share an edge if and only if $(u,v)$ is an edge in $G$ and this edge is only in this two routes. 
    We put a weight inbetween shared edges in a route so that there is a delay $k$ between two such edges.

    As in the previous proof, a $k$-coloring of $G$ gives a $k$-periodic schedule of $H$
    and conversly. Therefore if we can approximate the value of PRA  within a factor $f$,
    we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
    by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
    of finding a minimal coloring~\cite{zuckerman2006linear}.
    \end{proof}

>>>>

\graphicspath{{figures/}}
\newcommand\rmatching{${\cal R}$-matching\xspace}
\newcommand\mdelay{$\cal M$-delay\xspace}
\newcommand\matchedgraph{{\bf matched graph}}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{fact}{Fact}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}

@@

Consider an instance of Problem PRA, i.e., a digraph $G=(V,A)$, an assignment $\cal C$, a routing function $\cal R$ and a period $P$. 
The \emph{conflict depth} of an assignment $\cal C$ is the  number of arcs crossed by at least two routes in ${\cal R}_{\cal C}$; in other words it is the number of potential conflicts between these routes. 
The \emph{load} of  an assignment is the maximal number of routes sharing a same arc (i.e., the congestion of this arc).
It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.

We give two alternate proofs that PRA is $\NP$-complete.
The first one works for conflict depth $2$ and is minimal in this regards since we later prove that for conflict depth one,
it is easy to solve PRA. The second one reduces the problem to graph coloring and implies inapproximability. \\

 \begin{proposition}
Problem PRA is $\NP$-complete, for a routing with conflict depth two.
\end{proposition}
 \begin{proof}
  Let $H=(V,E)$ be a graph and $d$ its maximal degree. We want to determine whether $H$ is edge-colorable
  with $d$ or $d+1$ colors. We reduce this edge coloring problem to PRA. We define  from $H$ an instance $G,{\cal C}, {\cal R}, P$ as follows. For each 
  $v \in V$ there are two vertices in $G$  connected by an arc $(v_1,v_2)$ and none of these arcs are incident. The delay of these arcs is equal to $1$.
  The set $\cal C$ is made of couples of vertices $<s_{u,v}, l_{u,v}>$ for each edge $[u,v]$ in $H$ and the routes associated is ${\cal R} =s_{u,v},u_1,u_2,v_1,v_2,l_{u,v}$.  The delays of arcs $(s_{u,v},u_1)$ and $(v_2,l_{u,v})$ are equal to $d(d+1)-1$.

  Let $\phi$ be an edge coloring with $k$ colors of $H$. We can build a $k$-periodic affectation of $\cal C$ in $(G,{\cal R})$
  by assigning to the source $s_{u,v}$ of each route an offset  of $\phi(s_{u,v})$. Indeed, 
  if two routes $r_1$ and $r_2$ in ${\cal R}_{\cal C}$ share the same edge, say $(v_1,v_2)$ then they represent two edges $e_1$ and $e_2$ of $H$ incident  
  to the vertex $v$. Therefore $\lambda(v_1,r_1) = \phi(e_1) \mod k$ because the delays of the edges before $v_1$ sum to $d(d+1)$ or 
  $2(d(d+1))$ which are equal to $0$ modulo $k$ since $k=d$ or $k=d+1$. Thus $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k = \phi(e_1) - \phi(e_2) \mod k$
  and $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k > 0$ since $\phi(e_1) \neq \phi(e_2) $.

  Now consider a $k$-periodic affectation of $\cal C$ in $(G,{\cal R})$ . For each $[u,v]$ in $H$, we define $\phi(u,v)$ to be the offset of the route
  beginning at $s_{u,v}$ in ${\cal R}_{\cal C}$. For the same reasons as in the last paragraph, $\phi$ is an edge coloring with $k$ colors.
  Therefore we have reduced edge coloring which is $\NP$-hard~\cite{holyer1981np} to PRA which concludes the proof. 
 \end{proof}
Solving Problem PALL implies to solve PRA for an assignment ${\cal C}_{\rho}$ defined on $S$ and $L$ (see Section 2). Thus, we have the following corollary :

\begin{corollary}
Problem PALL is NP-Hard.
\end{corollary}

As another corollary of the previous proposition,  given $G$, $\cal R$, $P$ and two disjoint subsets $S$ and $L$ in $G$, the problem of  knowing if there is a matching $\rho$  from $L$ in $S$ such that the answer to problem PRA for instance $G,{\cal C_{\rho}},{\cal R}, P$ is  $\NP$-hard since checking a potential feasible solution for this problem implies to solve PRA.\\

Consider now MIN-PRA as the minimisation problem related to PRA, consisting in minimizing the peril $P$.

\begin{theorem}
 Problem MIN-PRA cannot be approximate within a factor $n^{1-o(1)}$ unless $\P = \NP$ even when the load is two
 and $n$ is the number of vertices.
\end{theorem}

\begin{proof}
 We reduce PRA to graph coloring. Let $H$ be a graph instance of the $k$-coloring problem. 
 We define $G$ in the following way: for each vertex $v$ in $H$, there is a route $r_v$ in $G$.
 Two routes $r_v$ and $r_u$ share an arc if and only if $[u,v]$ is an edge in $H$; this arc is the only one shared by these two routes.   We put delays inbetween shared arcs in a route so that there is a delay $k$ between two such arcs.

 As in the previous proof, a $k$-coloring of $H$ gives a $k$-periodic affectation in $G$
 and conversely. Therefore if we can approximate the minimum value of $P$  within a factor $f$,
 we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
 by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
 of finding a minimal coloring~\cite{zuckerman2006linear}.
\end{proof}

In particular, this reduction shows that even with small maximal load, the 
minimal period can be large.
